Enhancement of SDR in Thessaloniki

### 2024-04-12 high_aod/GHI_enh_03_process.tex
Commit 2024-04-12 16:14

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Warning in eval(ei, envir):

 ** Test is active!! ** 
\end{verbatim}

@@

C4 factor: 1.1 
C4 offset: 0 
\end{verbatim}

@@

\begin{verbatim}
Warning in eval(ei, envir): TEST IS ACTIVE !!
\end{verbatim}

  TEST IS ACTIVE  !!

2024-04-10 14:55:07 athan@tyler GHI_enh_02_ID_CE.R 6.972880 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-922.49 -337.13  -68.82  261.22 1657.04

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.886e+02  1.075e+02  -1.754   0.0802 .  
as.numeric(Date)  7.871e-07  8.610e-08   9.141   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 463.1 on 364 degrees of freedom
Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-922.49 -337.13  -68.82  261.22 1657.04

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.886e+02  1.075e+02  -1.754   0.0802 .  
ST_E_monthly$Date  7.871e-07  8.610e-08   9.141   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 463.1 on 364 degrees of freedom
Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-10 15:18:08 athan@tyler GHI_enh_02_ID_CE.R 17.930279 mins
\end{verbatim}

>>>>

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

@@

C4 factor: 1.11 
C4 offset: 0 
\end{verbatim}

@@

\begin{verbatim}
2024-04-12 11:43:50.1 athan@sagan GHI_enh_02_ID_CE.R 33.135529 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-403.26 -146.68  -25.16  113.64  654.68

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -8.280e+01  4.915e+01  -1.685   0.0929 .  
as.numeric(Date)  3.608e-07  3.928e-08   9.184   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 209.8 on 361 degrees of freedom
Multiple R-squared:  0.1894,    Adjusted R-squared:  0.1871 
F-statistic: 84.35 on 1 and 361 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-403.26 -146.68  -25.16  113.64  654.68

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -8.280e+01  4.915e+01  -1.685   0.0929 .  
ST_E_monthly$Date  3.608e-07  3.928e-08   9.184   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 209.8 on 361 degrees of freedom
Multiple R-squared:  0.1894,    Adjusted R-squared:  0.1871 
F-statistic: 84.35 on 1 and 361 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
R_LIB_USER
RANDOM_SEED
raw_input_data
RENV_PATHS_CACHE
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
TMPDIR
user_libs_path
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-12 11:51:07.2 athan@sagan GHI_enh_02_ID_CE.R 4.499965 mins
\end{verbatim}
